Exploring the evolution of stellar rotation using Galactic kinematics

### 2020-05-01 paper/ms63.tex
typo in citation

The mass dependence of magnetic activity lifetimes has been demonstrated
previously \racomment{for M dwarfs} \citep[\eg][]{west2008, reiners2009,
west2009, newton2017, kiman2019} and, if the detectability of a rotation
period is considered to be a magnetic activity proxy, then our results provide
further evidence for a mass-dependent activity lifetime.

>>>>

The mass dependence of magnetic activity lifetimes has been demonstrated
previously \racomment{for M dwarfs} \citep[\eg][]{west2008, reiners2008,
west2009, newton2017, kiman2019} and, if the detectability of a rotation
period is considered to be a magnetic activity proxy, then our results provide
further evidence for a mass-dependent activity lifetime.
